	\maketitle
	
	\begin{center}
		Prepared for \\
		NATIONAL AERONAUTICS AND SPACE ADMINISTRATION \\
		CONTRACT NAS 7-458 \\
		\vspace{1em}
		United Aircraft Research Laboratories \\
		UNITED AIRCRAFT CORPORATION
	\end{center}
	
	\newpage
	
	% --- ABSTRACT ---
	\begin{abstract}
		Two machine computational programs have been developed under NASA Contract 7-458 to calculate the steady-state temperature and reactant concentration distributions in typical catalyzed hydrazine decomposition reaction chambers.
		One program is based upon a one-dimensional model of the reactor system which describes the behavior of reactors having radially uniform injection profiles and catalyst bed configurations, while the other program is based upon a two-dimensional model which permits consideration of nonuniform radial injection and of catalyst bed configurations exhibiting both radial and axial nonuniformities.
		The one and two-dimensional models and the computer programs developed from these models are described in detail in this computer manual.
		The manual contains operating instructions for these programs as well as descriptions of input and output formats.
		Also included is a discussion of possible operations problems which might arise together with appropriate means for solving these problems.
	\end{abstract}
	
	% --- FOREWORD ---
	\section*{Foreword}
	This work was performed by United Aircraft Research Laboratories for the National Aeronautics and Space Administration under Contract NAS 7-458 initiated April 15, 1966.
	
	Included among those who cooperated in performance of the work under NAS 7-458 were Dr. A. S. Kesten, Program Manager, Dr. W. G. Burwell, Chief, Kinetics and Thermal Sciences Section, Mr. D. B. Smith, Project Analyst, and Mrs. E. J. Smith, Applied Mathematician.
	This work was conducted under program management of the NASA Chief, Liquid Propulsion Experimental Engineering Systems, NASA Headquarters, Washington, D. C., and the Technical Manager was Mr. T. W. Price, Jet Propulsion Laboratory, Pasadena, California.
	
	% --- SUMMARY ---
	\section*{Summary}
	A description is contained herein of two machine computational programs developed under Contract NAS 7-458 with the National Aeronautics and Space Administration.
	These programs represent one- and two-dimensional steady-state models of catalyzed hydrazine decomposition reaction chambers.
	Both of these models consider both thermal and catalytic decomposition of reactants, along with simultaneous heat and mass transfer between the free-gas phase and the gas within the pores of the catalyst pellets.
	The one-dimensional model of the reactor system describes the behavior of reactors having radially uniform injection profiles and catalyst bed configurations, while the two-dimensional model permits consideration of nonuniform radial injection and of catalyst bed configurations exhibiting both radial and axial nonuniformities.
	
	A general description of the one and two-dimensional models and a discussion of the machine programs developed from these models are contained in this manual.
	A description of input and output for both the one and two-dimensional steady-state programs are included in the discussion together with examples of typical data cases.
	Also included is a description of several operational problems which might be encountered while using the programs along with appropriate means for solving these problems.
	In addition, a short write-up of the subroutines contained in each deck is included along with general flow charts of the major routines.
	
	% --- INTRODUCTION ---
