	\section{Introduction}
	Under Contract NAS 7-458, the Research Laboratories of United Aircraft Corporation are performing analytical studies of the behavior of distributed-feed catalytic reactors for hydrazine decomposition.
	The specific objectives of this program are (a) to develop computer programs for predicting the temperature and concentration distributions in monopropellant hydrazine catalytic reactors in which hydrazine can be injected at arbitrary locations in the reaction chamber and (b) to perform calculations using these computer programs to demonstrate the effects of various system parameters on the performance of the reactor.
	
	Progress previously reported in the first annual report (Ref. 1) included the development of a computer program which describes the steady-state behavior of a continuous flow type reactor system in which complete radial mixing in the free-gas (or liquid) phase was assumed.
	Progress previously reported in the second annual report (Ref. 2) included an extension of the steady-state program to include radial as well as axial variations in temperature and concentrations in order to permit an analysis of various injection schemes and catalyst bed configurations which exhibit radial nonuniformities.
	These programs had been used to calculate temperature and reactant concentration distributions as functions of feed temperature, chamber pressure, mass flow rate distribution, catalyst size distribution, and embedded injector locations.
	As part of the third year of contract effort attention has been directed toward preparing a manual describing to potential users the operation of these computer programs.
	The manual includes a general description of the one and two-dimensional models as well as a detailed discussion of the machine programs representing these models.
	
	% --- DESCRIPTION OF ANALYSES ---
